The challenge and promise of software citation for credit, identification, discovery, and reuse

### 2016-04-07 SC-challenge.tex
and not or

Multiple organizations, including the WSSSPE Software Credit working group~\cite{WSSSPE1,WSSSPE2,WSSSPE3} and FORCE11 Software Citation Working Group~\citeyear{SCWG}, are working to standardize software citation practices.
Some of the observations and recommendations made here come from their efforts, which follow similar work by DataCite and the FORCE11~\citeN{DataCitation2014} to standardize research data citation practices.
Currently, services including Zenodo or fig\textbf{share} allow software developers to obtain DOIs for software; the former has a streamlined process~\citeyear{GitHubZenodo} to register DOIs for GitHub software releases.
The CodeMeta project~\cite{CodeMeta} is formalizing minimal metadata schemas in JSON and XML to connect existing software repositories, archives, and libraries (e.g., GitHub, fig\textbf{share}, Zenodo).

>>>>

Multiple organizations, including the WSSSPE Software Credit working group~\cite{WSSSPE1,WSSSPE2,WSSSPE3} and FORCE11 Software Citation Working Group~\citeyear{SCWG}, are working to standardize software citation practices.
Some of the observations and recommendations made here come from their efforts, which follow similar work by DataCite and the FORCE11~\citeN{DataCitation2014} to standardize research data citation practices.
Currently, services including Zenodo and fig\textbf{share} allow software developers to obtain DOIs for software; the former has a streamlined process~\citeyear{GitHubZenodo} to register DOIs for GitHub software releases.
The CodeMeta project~\cite{CodeMeta} is formalizing minimal metadata schemas in JSON and XML to connect existing software repositories, archives, and libraries (e.g., GitHub, fig\textbf{share}, Zenodo).
